### 2021-03-15 paper.Rmd
add slice tour figure
adjust layout

XXX figure should probably be combination of Fig 1 and 2 in @Laa2020-js

> figure 6 diagram illustrating projection vs slice

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.5\textwidth]{figures/scheidigger_nn_tour.png}
          \includegraphics[width=0.5\textwidth]{figures/scheidigger_umap_tour.png}
\caption{Left: A grand tour run on the output of a deep neural network model for classification. Right: A grand tour on UMAP components of a layer of deep neural network.}
\label{fig:tour-nn}
\end{figure*}

>>>>

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/slice_tour_left.jpg}
         \includegraphics[width=0.9\textwidth]{figures/slice_tour_right.jpg}
\caption{Ursula to write}
\label{fig:tour-slice}
\end{figure*}

@@

\begin{figure*}
   \centering
         \includegraphics[width=0.45\textwidth]{figures/scheidigger_nn_tour.png}
          \includegraphics[width=0.45\textwidth]{figures/scheidigger_umap_tour.png}
\caption{Left: A grand tour run on the output of a deep neural network model for classification. Right: A grand tour on UMAP components of a layer of deep neural network.}
\label{fig:tour-nn}
\end{figure*}
